Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-05-02 papers/eccv2018/4_results.tex
fixed some consistency issues

\noindent\textbf{Graph Generation.}
Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
This edge pruning is essential for the graph partitioning algorithm, which has a non-linear computational complexity dependence on the number of edges. 
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 764 compared to 974). 
Our pruning heuristic removes at least $3.5\times$ the number of edges on all datasets, achieving a maximum removal rate of $4.15\times$.
However, there are some adjacent over-segmented labels which are not considered.

>>>>

\noindent\textbf{Graph Generation}
Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
This edge pruning is essential for the graph partitioning algorithm, which has a non-linear computational complexity dependence on the number of edges. 
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 764 compared to 974). 
Our pruning heuristic removes at least $3.5\times$ the number of edges on all datasets, achieving a maximum removal rate of $4.15\times$.
However, there are some adjacent over-segmented labels which are not considered.

### 2018-05-02 papers/eccv2018/paper.tex
minor edits to first few sections, removed all red Xs
quals: added first draft for qualifying exam proposals
fixed some consistency issues

\begin{abstract}
% maybe better to cut to the point
%Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
%In the past decade in Connectomics, much progress has been made to classify neural membranes or affinities from the raw pixel and to watershed transform them into initial segments.
%Current state-of-the-art automatic methods classify neural membranes or affinities from the raw pixel followed by agglomeration methods to create full neuron reconstructions.
%An agglomerative segmentation algorithm merges initial pair of clusters.
Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging oversegmented regions.
%In the past deTraditionally, neuron segmentation from 3D electron microscopy (EM)
For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
Given the initial segmentation, we first create a graph with nodes corresponding to segment labels and edges identifying potential locations of split errors based on the skeleton structure of the segmentation.
Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 8.2\%.
\keywords{connectomics, biological constraints, region merge, skeletonization, deep learning, lifted multicut}
\end{abstract}

>>>>

\begin{abstract}
% maybe better to cut to the point
%Advancements in electron microscopy image acquisition have created connectomics datasets terabytes in size making manual reconstruction of neuronal structures infeasible.
%In the past decade in Connectomics, much progress has been made to classify neural membranes or affinities from the raw pixel and to watershed transform them into initial segments.
%Current state-of-the-art automatic methods classify neural membranes or affinities from the raw pixel followed by agglomeration methods to create full neuron reconstructions.
%An agglomerative segmentation algorithm merges initial pair of clusters.
Current state-of-the-art connectome reconstruction pipelines have two major steps: initial pixel-based segmentation with affinity prediction and watershed transform, and refined segmentation by merging over-segmented regions.
For the region merging, most methods neglect geometric and topological constraints that are inherent in the graph structure of neural wiring diagrams.
In this work, we use a biologically-constrained graph-based method to better reconstruct neural pathways.
Given the initial segmentation, we first create a graph with nodes corresponding to segment labels and edges identifying potential locations of split errors based on the skeleton structure of the segmentation.
Next, we train a convolutional neural network to capture the geometric properties of segment connections and produce edge weights as the probability of merging two nodes.
Finally, we formulate the region merging as a lifted multicut partitioning problem with topological constraints to avoid cycles.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of 8.2\%.
\keywords{connectomics, biological constraints, region merge, skeletonization, deep learning, lifted multicut}
\end{abstract}
